---
title: "week1-exercise"
author: "az"
date: "9/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r set up}
vignette(package='cowsay')
vignette('cowsay_tutorial', package='cowsay')
library(cowsay)
```

Make a cat say, “FEED ME”
```{r question 1}
say("FEED ME")   # as default value for argument "by" is "cat"
```

Make a shark say “Hello world!”
```{r question 2}
say("Hello world!", "shark")
```

Make anything produce a famous quote
```{r question 3}
say("Keep moving and Love abundantly", "owl")
```

Make a clippy warn the user about the impending apocalypse
```{r question 4}
say("World gonna end, you sure?", "clippy")
```

Make a cat produce a random quote from an R coder. You should get a different quote every time you run the code (hint: read the documentation for cowsay::say()).
```{r question 5}
say("fortune")
```

Define a variable creature and assign to it the value of one of the types of creatures accepted by the say() function. Then use the variable to output the current time.
```{r question 6}
creature <- "owl"
say('time', creature)
```

Change the value of the variable creature to some other thing, and make it display the time using the date() function in base R.
```{r question 7}
creature <- 'snowman'
say(date(), creature)
```