---
title: "week1-notes"
author: "az"
date: "9/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Week 1: Intro to R

### 1.Intro to R Part 1

#### Tying in commands: interacting with the console

##### storing results in a variable
```{r storing results in a variable}
tempt <- 2 + 2
```


##### whitespace
```{r whitespace}
library(cowsay)
say("This function call far too wide to fit all on one line",
    "poop")
```
##### workspace
```{r workspace}
ls()
rm("tempt")
rm(list=ls())
```

##### vectors
```{r vectors}
v1 <- c(1,2,3)
```

##### vectorized operations
```{r vectorized operations}
iq <- c(86, 101, 127, 99)
std_iq <- (iq - 100)/15
std_iq
```

##### function syntax
Generic syntax: `functionname(arg1, arg2, arg3, ...)`
Each function has *named arguments*: those without default values are mandatory, those with these values are optional. 

```{r function syntax}
# function rnorm() generates random numbers from the standard normal distribution
#rnorm() will return error as rnorm(n, mean = 0, sd = 1), no default for n
rnorm(3)
rnorm(3, 100)
rnorm(3, sd = 100)
```

#### add on packages
notice the difference between *installing a package* and *loading a package*
```{r add on packages}
#install.packages('fortunes')
library(fortunes)
fortune()
```

#### help
```{r help, echo=FALSE}
help('say')                    # 1 (if package is loaded)
?say                           # 2
help('say', package='cowsay')  # 3
??help                         # 4 (search for help files)
help.start()                   # 5 (start up help in browser)

```

### 2.Intro to R Part 

#### Organizing a project
##### Work Directory
To set work directory:
1. `Session` | `Set Working Directory`
2. in console, `setwd('')`

* Script should only reference files from (1) web (2) working dir (3) subdir
* load file using relative path (forward slashes)

#### Structuring your script
To develop reproducible R script, there are certain conventional structure to follow:
1. load all add-on packages
2. define custom functions
3. import data
4. perform the analysis
5. save your work

* a single chunk for each output
```{r code chunk, message=FALSE, warning=FALSE}
# suppress messages and warnings in code chunks
```

#### Basic data types
Four main basic data types in R:
1. `character`
2. `integer` e.g. `10L`
3. `double` aka `numeric`, e.g. `10`, `3.13`
4. `logical`

```{r basic data types}
class(.5)      # class() to know the data type of something
class(10)
class(10L)
mode(c(1,2,3)) # mode() function is specifically for vectors
```

#### Basic container types
vector: an ordered container of elements of the same data type, a variable to store multiple values (elements)
* when we entered a single number, R created a vector with a single element

```{r vector}
vec1 <- 200:400
vec2 <- c(1L, 19L, 37L, 55L)
vec1[vec2]
# vectors can be named
vec3 <- c(first=77.9, second=-13.2, third=100.1)
vec3
vec3[c("second","third","first")]
vec3[c(TRUE, FALSE, TRUE)]
# other ways of creating vectors
rep(0,10)
rep(c(1L,3L),7)
evens <- rep(c(FALSE, TRUE), 100)
vec1[evens]

```
List: a collection of data of different data types

```{r list}
albums <- 
  list(
    Michael_Jackson = c(
      "Off the Wall",
      "Thriller",
      "Bad",
      "Dangerous"
    ),
    Nirvana = c(
      "Bleach",
      "Nevermind",
      "In Utero"
    )
  )  
albums[1]
albums$Nirvana
```


#### Tabular data

Tabular data, stored in `data.frame` or `tibble` are a special type of list, , in which each column has the same number of elements.
There are three ways to look at the tibble `View()`, `print()`, `glimpse()`
```{r tibble}
months <- tibble(ID = 1:12,
                 name = c("Jan", "Feb", "Mar", "Apr",
                          "May", "Jun", "Jul", "Aug",
                          "Sep", "Oct", "Nov", "Dec"))
dim(months)
```

#### Importing data

```{r data import}
library(tidyverse)
data <- read_csv("C:/Users/ashle/Job.Intern.Lab/CDL/FormEx/formex6_wide_new.csv")
# the first line of the data is used as the column names
read_csv("a,b,c
         1,2,3
         4,5,6")
# to tweak for multiple lines of meta data
read_csv("first line to skip
         second line to skip
         x,y,z
         1,2,3", skip=2)
read_csv("# A comment to skip
         x,y,z
         1,2,3", comment="#")
# to tweak for an absence of column names
read_csv("1,2,3\n4,5,6", col_names=FALSE)
read_csv("1,2,3\n4,5,6", col_names=c("x","y","z"))
# to tweak for missing values
read_csv("1,2,3\n4,5,.", na=".")
```      


#### Pipes
Pipes(`%>%`) strings together a sequence of commands in 
```{r pipes}
x <- sample(1:10, 5, replace=TRUE)
y <- unique(x)
sort(y, TRUE)
# rewrite using pipes
sample(1:10, 5, replace=TRUE) %>%      # the result is passed to unique()
  unique() %>%          # always as the first argument
  sort(TRUE)
```